```{r}
class(sin)
```
# ∫ = option and B
```{r}
3 < "four"
3 < "quatre"
3 < "deux"
3 < "two"
```
# Why does it say TRUE? 
```{r}
"three"< "zwei"
as.character("hi")
```
# "AS.CHARACTER" turns whatever input into a character string output. 
```{r}
as.character(word)
as.character("FALSE")
as.numeric(4)
as.numeric("two") 
```
# AS.NUMERIC "as.numeric" only takes numbers and gives back a logical number. 
```{r}
3 == "dog"
3==2
"TRUE" == "TRUE"
"TRUE" == "FALSE"
"T" == "T"
```
# SEQUENCE: numeric in, numeric out, use : or , 
```{r}
seq(1:10)
```
# [] two inputs: vector or list and an index
```{r}
v[ v<5 ]

Fred <- (c(7,5,6))
`any name at alll here` <-c(7,5,2)
v <- 1:10
v[4]
```
# PASTE(): Each input gets converted to a string
```{r}
paste(3,5)
```
# STRSPLIT(): Splitting Strings
```{r}
help(strsplit)
strsplit("What kind of thing?", "n")
strsplit("ffffffhifffff", "f")
strsplit(c("No n's this", "What kind of thing?"), "n")
```
# LIST(), one bracket: list, double brackets: contents of slot 3 AND Fred()
```{r}
list("Matrix", c(1,2,3), FALSE)
fred <-list("Matrix", c(1,2,3), FALSE)
fred[[3]]
fred[3]
fred[4] <- "now is the time"
fred[4]
fred[-20]
fred[10] <- "ten"
fred
fred <- list(hamline="Matrix", carleton=c(a=1,b=2,c=3), mac=FALSE)
fred
fred[["carleton"]]
fred[[]]
fred[["carleton"]]['c']
fred[["carleton"]][['c']]
```
#GREP(), GREPL(), SUB()
```{r}
c("becomes", "ages")
grep("b", c("becomes", "ages"))
grepl("b", c("becomes", "ages"))
v <- c("becomes", "ages")
sub("e","*", v)
gsub("[aeiou]", "*", v)
w <- c("what the fudge")
sub("u", "*", w)
grepl("[aeiou]", v)
grepl("^[b].*[s]$",v)
```
# CROSSWORDS: finding words
```{r}
words <- readLines(url("http://dtkaplan.github.io/ScientificComputing/Syllabus/Daily/Day-07/word_list_moby_crossword-flat/word_list_moby_crossword.flat.txt"))
class(words)
length(words)
grep("^b.q.$", words)
words[grep("^b.q...$", words)]
words[grep("^a.li....r$", words)]
```

