# Recursion
==========

## Loop of Fibonacci Numbers
#### Given Example:
```{r}
fibLoop <- function(n) {
    Ffirst <- 0
    Fsecond <- 1
    for (k in 2:n) {
        newF <- Ffirst + Fsecond
        Ffirst <- Fsecond
        Fsecond <- newF
    }
    return(newF)
}
```
Testing
```{r}
fibLoop(5)
fibLoop(20)
```

#### Loop where the state is maintained by a vector of n+1 slots, with the first two slots initialized to 0 and 1 respectively
```{r}
fibLoop2<-function(n){
  sofar=c(0,1)
  for(k in 3:n){
  sofar[k]<-sofar[k-1]+sofar[k-2]
  sofar[k+1]<-sofar[k]+sofar[k-1]
  }
  return(sofar[k+1])
  }
```
Testing
```{r}
fibLoop2(5)
fibLoop2(20)
```

#### Returns all fibonacci numbers n and below:
```{r}
fibLoop2<-function(n){
  sofar=c(0,1)
  for(k in 3:n){
  sofar[k]<-sofar[k-1]+sofar[k-2]
  sofar[k+1]<-sofar[k]+sofar[k-1]
  }
  return(sofar)
  }

fibLoop2(5)
fibLoop2(20)
```

## A Recursive structure for Fn
#### Given Example:
```{r}
fibRecurse <- function(n) {
    if (n == 1) {
        return(1)
    } else {
        if (n == 0) 
            return(0)
    }
    thisF <- fibRecurse(n - 1) + fibRecurse(n - 2)
    return(thisF)
}

fibRecurse(5)
fibRecurse(20)
```

#### More concise way:
```{r}
fib1 <- function(n) {
    if (n < 2) 
        return(n)
    return(fib1(n - 1) + fib1(n - 2))
}
```
Testing
```{r}
fib1(5)
fib1(20)
```

## Exercises
#### Write a recursive function to add up the numbers from n to zero:
```{r}
addNSeq <- function(n) {
  if(n==1){
    return(1)}
  else{
    if(n==0){
      return(0)
    }
  }
  sum <- addNSeq(n-1)+n
  return(sum)
  }
```
Testing
```{r}
addNSeq(4)
addNSeq(7)
```

#### Loop
```{r}
addNSeqLoop<-function(n){
  sum <- 0
  for(k in 1:n){
    sum <- n-k + sum
  }
  return(sum+n)
}
```
Testing
```{r}
addNSeqLoop(3)
addNSeqLoop(5)
```

#### Simple Vector
```{r}
addNSeqLoop<-function(n){
  vect <- 1:n
  return(sum(vect))
}
```
Testing
```{r}
addNSeqLoop(5)
addNSeqLoop(8)
```

#### Write a recursive function to add up all the numbers in a vector
```{r}
addRecursively <- function(v) {
  if(length(v)==1){
    return(v[1])
  }
  sum <- addRecursively(v[-length(v)])+v[length(v)]
  return(sum)
  }
```
Testing
```{r}
addRecursively(c(3,6,9))
addRecursively(c(4,7,10))
```

#### Loop
```{r}
addRecLoop<-function(v){
  sum<-0
  for(k in 1:length(v)){
    sum <- v[k]+sum
  }
  return(sum)
}
```
Testing
```{r}
addRecLoop(c(3,5,8))
addRecLoop(c(2,5,9))
```

#### Simple vectorized operational version
```{r}
addSimple<-function(v){
  sum(v)
}

addRecSimple(c(1,2,3))
addRecSimple(c(5,7,9))
```

## Natural Settings for Recursion
```{r}
simpleRiemann <- function(f, a = 0, b = 1, n = 3) {
    rectangleWidth = (b - a)/n
    midpoints <- seq(a + rectangleWidth/2, b - rectangleWidth/2, length = n)
    rectangleAreas <- sapply(midpoints, f) * rectangleWidth
    return(sum(rectangleAreas))
}
```

```{r}
integrateRiemann <- function(f, a = 0, b = 1) {
    nbins <- 5
    biggerBins <- simpleRiemann(f, a = a, b = b, n = nbins)
    for (k in 1:5) {
        nbins <- nbins * 10  # much smaller bins
        smallerBins <- simpleRiemann(f, a = a, b = b, n = nbins)
        if (abs(smallerBins - biggerBins) < 1e-05) 
            break
        biggerBins <- smallerBins
    }
    return(smallerBins)
}
```
Testing! 
```{r}
integrateRiemann(function(x) {
    3 * x
}, a = 0, b = 10)
```
Testing! 
```{r}
integrateRiemann(function(x) {
    3 * x^2
}, a = 0, b = 10)
```

## Your Tasks
#### Modify integrateRecursive()
```{r}
integrateRecursive <- function(f, a = 0, b = 1) {
    biggerBins <- simpleRiemann(f, a = a, b = b, n = 5)
    smallerBins <- simpleRiemann(f, a = a, b = b, n = 10)
    if (abs(biggerBins - smallerBins) < 1e-05) 
        return(smallerBins) else {
        mid <- (a + b)/2
        total <- integrateRecursive(f, a = a, b = mid) + integrateRecursive(f, 
            a = mid, b = b)
        if(n==10000){break}
        return(total)
    }
}
```

#### Demo your Program
```{r}
integrateRecursive(function(x) {
    4 * x
}, a = 0, b = 10)
```
$\int\limits_{0}^{10} 4*x dx = 200$

```{r}
integrateRiemann(function(x) {
     x^6
}, a = 0, b = 10)
```
$\int\limits_{0}^{10} 4*x^6 dx = 1428571$

#### A Better Simple Integrator
```{r}
gaussQuadrature <- function(f, a = 0, b = 1) {
    # Just 4 function evaluations!

    # 'Magic' values on z in [0,1]
    z <- c(c(-1, 1) * sqrt((3 - 2 * sqrt(6/5))/7), c(-1, 1) * sqrt((3 + 2 * 
        sqrt(6/5))/7))
    # weights (analogous to bin width)
    w <- c(rep((18 + sqrt(30))/36, 2), rep((18 - sqrt(30))/36, 2))
    # Translate to interval x in [a,b]
    x <- ((b - a)/2) * z + (a + b)/2
    # evaluate the function at x, multiply by weights, and sum
    return(((b - a)/2) * sum(w * sapply(x, f)))
}
```
Testing
```{r}
gaussQuadrature(function(x) 3 + 0 * x, 0, 10)
gaussQuadrature(function(x) 3 * x, 0, 10)
gaussQuadrature(function(x) 3 * x^2, 0, 10)
```

#### What power of x does gaussQuadrature fail for? Answer: 318
```{r}
gaussQuadrature(function(x) x^317,0,10)
gaussQuadrature(function(x) x^318,0,10)
```

#### Test out gaussQuadrature() on sine and cosine functions, with a=0 and b successively larger, that is, b=0.1, b=1.0, and so on. How wide can you make the interval, before the result of gaussQuadrature() is not accurate? Answer: $2*pi+0.1$
```{r}
gaussQuadrature(function(x) sin(x),0,2*pi+0.1)
```
$\int\limits_{0}^{2*pi+0.1}\sin{x}dx = 0.004995$

#### Re-implement integrateRecursive() using gaussQuadrature() as the base integrator. You'll have to be creative, since you can't change the number of bins as in the test-for-simple part of integrateRecursive(). Show that your function works on trigonometric functions with b big.
```{r}
integrateRecursive2 <- function(f, a = 0, b = 1) {
    biggerBins <- gaussQuadrature(f, a = a, b = b, n = 5)
    smallerBins <- gaussQuadrature(f, a = a, b = b, n = 10)
    if (abs(biggerBins - smallerBins) < 1e-05) 
        return(smallerBins) else {
        mid <- (a + b)/2
        total <- integrateRecursive2(f, a = a, b = mid) + integrateRecursive2(f, 
            a = mid, b = b)
        if(n==10000){break}
        return(total)
    }
}
```

### Plotting a function
```{r}

plotF<-function(f,a=0,b=1){
  diff<-(b-a)
  x<-seq(a,b,length=(diff*100))
  y<-f(x)
  plot(x,y,xlab="x",ylab="f(x)",main="plotF",type="l",pch=20,cex=.2,col="red") 
}

plotF(function(x)x+x^3,-5,5)
```
